\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/architecture.tex
Added VM experiment to limitations and Pass on Conclusion

>>>>

\subsubsection{Hypervisors}
For virtual environments that provide guests significant periods of access to 
hardware resources, we have found that \speculake is viable in certain configurations.

\texttt{Guest -> Guest (internal)} - When both trigger and payload are run internal to
a single virtual machine the branch prediction is successfully trained in the payload
program, though at a notably reduced hit rate. This can be overcome by using an 
increased number of iterations to establish confidence.

\texttt{Guest -> Host} - In a configuration where trigger runs on the guest while the 
payload runs on the host we have found that \speculake also successfully trains the 
branch predictor well enough retreive a signal. Again, this signal is significantly
reduced, implying the hypercall context swtich from guest to host requires some 
overhead. We note that processor affinity in a guest is not mapped to processor 
affinity in the host, as the host assigns the vm to any available CPU, though 
eventually the hypervisor will assign the vm back to the same core as the payload 
program allowing progress to continue.

\texttt{Host -> Guest} - When trigger runs on the host attempting to train the 
branch predictor to influence a payload process in a guest we have found that 
the payload receives no signal. This implies that the hypercall context switch 
from the host to the guest is heavier and has a larger impact on branch history. 
This matches with work done by the Project Zero team at Google which found that 
hypervisors can be fingerprinted from within a vm using the branch 
predictor~\cite{project_zero}.

\texttt{Guest -> Guest (external)} - Configurations where trigger and payload 
run on coresident virtual machines similarly show no signal for the same 
reasons that host to guest \speculake fails. However, this has the added difficulty
that virtual machines must be run on the same core or on a pair of 
hyperthreaded cores.

### 2018-05-08 paper/discussion.tex
Added VM experiment to limitations and Pass on Conclusion

Alternatively multiple triggers could be used make individual state changes in
the payload program, and write in data from a local, or (as demonstrated in 
section~\ref{subsec:nested-spec}) remote processes. For example, a payload program
can check a series of three distinct jump patterns corresponding to three different 
triggers. If the first trigger is detected the payload shifts in a 1 to the state; if
the second is detected it shifts in a 0. If the third trigger is detected it 
discontinues listening to the three triggers and proceeds with other computation. 
This could be a direct form of \speculake using emulation and decryption 
or more traditional malicious behavior. Using this method a payload program can
be distributed without the encrypted data section all together, instead having 
the data written into the process at run-time without ever connecting out to any 
other resource.

@@

\subsubsection{Alternative Applications}
We have proposed the \speculake model as a new malware threat, however, this model
of hidden computation applies more broadly. As of now there are no ways of 
debugging speculative computation meaning that the computation done there is effectively
isolated as with trusted execution environments. The security provided by the obfuscated 
key schedule makes \speculake useful in the domains of Digital Rights Management (DRM)
and whitebox cryptography more generally. 
%% Approximate Computing

>>>>

Alternatively multiple triggers could be used make individual state changes in
the payload program, and write in data from a local, or (as demonstrated in 
section~\ref{subsec:openssl}) remote processes. For example, a payload program
can check a series of three distinct jump patterns corresponding to three different 
triggers. If the first trigger is detected the payload shifts in a 1 to the state; if
the second is detected it shifts in a 0. If the third trigger is detected it 
discontinues listening to the three triggers and proceeds with other computation. 
This could be a direct form of \speculake using emulation and decryption 
or more traditional malicious behavior. Using this method a payload program can
be distributed without the encrypted data section all together, instead having 
the data written into the process at run-time without ever connecting out to any 
other resource.

@@

\subsubsection{Alternative Applications}
We have proposed the \speculake model as a new malware threat, however, this model
of hidden computation applies more broadly. As of now there are no ways of 
debugging speculative computation meaning that the computation done there is effectively
isolated as with trusted execution environments. The security provided by the obfuscated 
key schedule makes \speculake useful in the domains of Digital Rights Management (DRM)
and whitebox cryptography, and apprimate computing fields. 
%% Approximate Computing
